---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jingchuan Xu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Analyzing Marriage Licence Statistics data from Toronto using R and Quarto. It requires simulating data from a Poisson distribution, gathering real data from Open Data Toronto, and cleaning it using R scripts. A report with graphs and citations will be generated in Quarto, and the final document will include a title, author, and abstract. The workflow culminates in updating the README and submitting a Gist with GitHub links to repositories from the group."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


